Pillar 1 - Sequential Pattern Mining

### 2019-01-30 Pillar 1 - Sequential Pattern Mining.Rmd

AR_Taken <- my_apriori(transactions_Taken)

#
# Save association rules
AR <- list(
    AR = AR,
    AR_PF = AR_PF,
    AR_HL = AR_HL,
    AR_Taken = AR_Taken
    )

save(AR, file = "App/AR.RDATA")

rm(clean_AR, my_apriori,
   transactions, transactions_PF, transactions_HL,
   course_id_fail, course_id_low,
   AR, AR_PF, AR_HL, AR_Taken)

>>>>

AR_not_taken <- my_apriori(transactions_Taken)

#
# Save association rules
save(AR_taken, AR_PF, AR_HL, AR_not_taken,
     file = "App/AR.RDATA")

rm(clean_AR, my_apriori,
   transactions, transactions_PF, transactions_HL,
   course_id_fail, course_id_low,
   AR_taken, AR_PF, AR_HL, AR_not_taken)
